Flowchart of Current Algorithm

### 2008-10-24 docs/flowchart/flowchart.tex
update how the enthalpy update looks for spherical
fix an equation reference

\item Update the enthalpy.  The full enthalpy equation is 
\MarginPar{we should say something about {\tt use\_tfromp}, and {\tt do\_eos\_h\_above\_cutoff}}
  \begin{equation}
  \frac{\partial (\rho h)}{\partial t}  = - \nablab \cdotb (\Ub \rho h)
+ \frac{Dp_0}{Dt} + \nabla\cdot\kth\nabla T + \rho \Hnuc + \rho \Hext 
\enskip , \label{eq:rhohupd} 
  \end{equation}
Here we consider only the advection, neglecting the reaction terms and thermal diffusion terms,
and solve a discretized version of
  \begin{equation}
  \frac{\partial (\rho h)}{\partial t}  = - \nablab \cdotb (\Ub \rho h)
+ \frac{Dp_0}{Dt} 
\enskip , \label{eq:rhohupdadv} 
  \end{equation}

@@

  \item Evolve $(\rho h)^{(1)} \rightarrow (\rho h)^{(2'),\star}$ without
  explicitly including the reaction terms,
  \begin{eqnarray}
  (\rho h)^{(2'),\star} &=& (\rho h)^{(1)} - \dt \; \left\{ \nablab
      \cdotb \left[ \left(\uadvone+w_0^{\nph,\star} \er\right) (\rho
      h)^{(1),\nph,\star} \right] \right\} \nonumber \\ && + \dt \;
    \left(\uadvone \cdotb \er\right) \left(\frac{\partial
      p_0}{\partial r} \right)^{n} + \dt \; \psi^{\nph,*} \enskip ,
  \end{eqnarray}
  \MarginPar{we should also show the update in the case that $(\rho h)'$ is the flux}
  \end{enumerate}

@@

\item Diffuse the enthalpy through a time interval of $\dt$.  Here we begin
with the enthalpy equation (eq.~[\ref{eq:rhohup}]), but consider only the 
diffusion terms,
\begin{equation}
  \frac{\partial (\rho h)}{\partial t}  = 
 \nabla\cdot\kth\nabla T 
\enskip . \label{eq:rhohupdthermal} 
  \end{equation}
We can recast this as an enthalpy-diffusion equation by applying the
chain-rule to $h(p_0,T,X_k)$,
\begin{equation}
\nabla h = h_p \nabla p_0 + c_p \nabla T + \sum_k \xi_k \nabla X_k \enskip ,
\end{equation}
giving
\begin{equation}
  \frac{\partial (\rho h)}{\partial t}  = 
 \nabla\cdot \frac{\kth}{c_p}\nabla h -  
 \sum_k \nabla\cdot \frac{\xi_k \kth}{c_p}\nabla X_k -
 \nabla\cdot \frac{h_p \kth}{c_p}\nabla p_0 
\enskip . \label{eq:rhohupdthermal2} 
  \end{equation}

@@

   \item Evolve $(\rho h)^{(1)} \rightarrow (\rho h)^{(2)}$ without
     explicitly including the reaction terms,
\begin{eqnarray}
(\rho h)^{(2')} &=& (\rho h)^{(1)} - \dt \; \left\{ \nablab \cdotb \left[ \left(\uadvtwo+w_0^{\nph} \er\right)  
(\rho h)^{(1),\nph} \right] \right\} \nonumber \\
&& + \frac{\dt}{2} \; \left(\uadvtwo \cdotb \er\right)
\left [ \left(\frac{\partial p_0}{\partial r} \right)^{n}
      + \left(\frac{\partial p_0}{\partial r} \right)^{n+1}  \right ] 
+ \dt \; \psi^{\nph} \enskip ,
\end{eqnarray}

>>>>

\item Update the enthalpy.  The full enthalpy equation is 
\MarginPar{we should say something about {\tt use\_tfromp}, and {\tt do\_eos\_h\_above\_cutoff}}
  \begin{equation}
  \frac{\partial (\rho h)}{\partial t}  = - \nablab \cdotb (\Ub \rho h)
+ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} + \nabla\cdot\kth\nabla T + \rho \Hnuc + \rho \Hext 
\enskip , \label{eq:rhohupd} 
  \end{equation}
Here we consider only the advection, neglecting the reaction terms and thermal diffusion terms,
and solve a discretized version of
  \begin{equation}
  \frac{\partial (\rho h)}{\partial t}  = - \nablab \cdotb (\Ub \rho h)
+ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} 
\enskip , \label{eq:rhohupdadv} 
  \end{equation}
For spherical flows, experience has shown that solving the algebraically-equivalent form
\begin{equation}
  \frac{\partial (\rho h)}{\partial t}  = - \nablab \cdotb (\Ub \rho h)
+ \psi + \nabla \cdot (\Ubt p_0) - p_0 \nabla \cdot \Ubt  
\enskip , \label{eq:rhohupdadv2} 
\end{equation}
results in a better solution.

@@

  \item Evolve $(\rho h)^{(1)} \rightarrow (\rho h)^{(2'),\star}$ without
  explicitly including the reaction terms,

\begin{description}
\item[plane-parallel:]

  \begin{eqnarray}
  (\rho h)^{(2'),\star} &=& (\rho h)^{(1)} - \dt \; \left\{ \nablab
      \cdotb \left[ \left(\uadvone+w_0^{\nph,\star} \er\right) (\rho
      h)^{(1),\nph,\star} \right] \right\} \nonumber \\ && + \dt \;
    \left(\uadvone \cdotb \er\right) \left(\frac{\partial
      p_0}{\partial r} \right)^{n} + \dt \; \psi^{\nph,*} \enskip ,
  \end{eqnarray}
  \MarginPar{we should also show the update in the case that $(\rho h)'$ is the flux}

  \begin{eqnarray}
  (\rho h)^{(2'),\star} &=& (\rho h)^{(1)} - \dt \; \left\{ \nablab
      \cdotb \left[ \left(\uadvone+w_0^{\nph,\star} \er\right) (\rho
      h)^{(1),\nph,\star} \right] \right\} \nonumber \\ 
    && + \dt \; \left \{ \nabla \cdot \left (\uadvone p_0^{n} \right ) 
       - p_0^{n} \nabla \cdot \uadvone \right \} \nonumber \\
    && + \dt \; \psi^{\nph,*} \enskip ,
  \end{eqnarray}

\MarginPar{is it really $p_0^n$ here and not $p_0^{n+1/2}$?}
\end{description}

@@

\item Diffuse the enthalpy through a time interval of $\dt$.  Here we begin
with the enthalpy equation (eq.~[\ref{eq:rhohupd}]), but consider only the 
diffusion terms,
\begin{equation}
  \frac{\partial (\rho h)}{\partial t}  = 
 \nabla\cdot\kth\nabla T 
\enskip . \label{eq:rhohupdthermal} 
  \end{equation}
We can recast this as an enthalpy-diffusion equation by applying the
chain-rule to $h(p_0,T,X_k)$,
\begin{equation}
\nabla h = h_p \nabla p_0 + c_p \nabla T + \sum_k \xi_k \nabla X_k \enskip ,
\end{equation}
giving
\begin{equation}
  \frac{\partial (\rho h)}{\partial t}  = 
 \nabla\cdot \frac{\kth}{c_p}\nabla h -  
 \sum_k \nabla\cdot \frac{\xi_k \kth}{c_p}\nabla X_k -
 \nabla\cdot \frac{h_p \kth}{c_p}\nabla p_0 
\enskip . \label{eq:rhohupdthermal2} 
  \end{equation}

@@

   \item Evolve $(\rho h)^{(1)} \rightarrow (\rho h)^{(2)}$ without
     explicitly including the reaction terms,

\begin{description}
\item[plane-parallel:]

\begin{eqnarray}
(\rho h)^{(2')} &=& (\rho h)^{(1)} - \dt \; \left\{ \nablab \cdotb \left[ \left(\uadvtwo+w_0^{\nph} \er\right)  
(\rho h)^{(1),\nph} \right] \right\} \nonumber \\
&& + \frac{\dt}{2} \; \left(\uadvtwo \cdotb \er\right)
\left [ \left(\frac{\partial p_0}{\partial r} \right)^{n}
      + \left(\frac{\partial p_0}{\partial r} \right)^{n+1}  \right ] 
+ \dt \; \psi^{\nph} \enskip ,
\end{eqnarray}

\begin{eqnarray}
(\rho h)^{(2')} &=& (\rho h)^{(1)} - \dt \; \left\{ \nablab \cdotb \left[ \left(\uadvtwo+w_0^{\nph} \er\right)  
(\rho h)^{(1),\nph} \right] \right\} \nonumber \\
    && + \dt \; \left \{ \nabla \cdot \left (\uadvtwo p_0^{n+1/2} \right ) 
       - p_0^{n+1/2} \nabla \cdot \uadvtwo \right \} \nonumber \\
    && + \dt \; \psi^{\nph} \enskip ,
\end{eqnarray}
